Actuator line modeling of vertical-axis turbines

### 2016-08-27 paper.tex
Shrink mesh fig in light of review 1
Note that rotor drag is often called thrust
Add line numbers to manuscript
Fix incomplete sentence

@@

@@

    \includegraphics[width=0.8\textwidth]{thesis_alm-mesh}

@@

Power and drag coefficient curves are plotted for the UNH-RVAT in
Figure~\ref{fig:RVAT-ALM-perf-curves}. The ALM was successful at predicting the
performance tip speed ratios up to $\lambda_0$, which suggests that dynamic
stall was being modeled accurately, but $C_P$ was overpredicted at high
$\lambda$. This may have been caused by the omission of additional parasitic
drag sources such as roughness from exposed bolt heads located far enough from
the axis to have a large effect at high rotation rates, or an underestimation of
the blade--strut connection corner drag coefficient. In
\cite{Rawlings2008,Bachant2016-RM2-paper} it was shown how these losses can be
significant even with carefully smoothed struts and strut-blade connections.
Overprediction of performance at high tip speed ratio could also be a
consequence of the Leishman--Beddoes dynamic stall model, which can also be seen
in the Darrieus VAWT momentum model results shown in Figure 6.70 of
\cite{Para2002}.

@@

Thus, the UNH-RVAT baseline case was simulated using the Smagorinsky LES
turbulence model \cite{Smagorinsky1963}, which was the first of its kind, and
serves as a good standard for LES modeling since its behavior is well-reported
in the literature. Default Smagorinsky model coefficients were used, LES filter
width was set as the cube root of the local cell volume. The tip speed ratio was
set to oscillate sinusoidally about $\lambda_0$ with a 0.19 magnitude and the
angle of the first peak at 1.4 radians---similar to the rotation presribed in
the blade-resolved RANS simulations discussed in \cite{Bachant2016-BR-CFD}.

>>>>

\usepackage{lineno}

@@

\linenumbers

@@

    \includegraphics[width=0.65\textwidth]{thesis_alm-mesh}

@@

Power and overall rotor drag (a.k.a. thrust) coefficient curves are plotted for
the UNH-RVAT in Figure~\ref{fig:RVAT-ALM-perf-curves}. The ALM was successful at
predicting the performance tip speed ratios up to $\lambda_0$, which suggests
that dynamic stall was being modeled accurately, but $C_P$ was overpredicted at
high $\lambda$. This may have been caused by the omission of additional
parasitic drag sources such as roughness from exposed bolt heads located far
enough from the axis to have a large effect at high rotation rates, or an
underestimation of the blade--strut connection corner drag coefficient. In
\cite{Rawlings2008,Bachant2016-RM2-paper} it was shown how these losses can be
significant even with carefully smoothed struts and strut-blade connections.
Overprediction of performance at high tip speed ratio could also be a
consequence of the Leishman--Beddoes dynamic stall model, which can also be seen
in the Darrieus VAWT momentum model results shown in Figure 6.70 of
\cite{Para2002}.

@@

Thus, the UNH-RVAT baseline case was simulated using the Smagorinsky LES
turbulence model \cite{Smagorinsky1963}, which was the first of its kind, and
serves as a good standard for LES modeling since its behavior is well-reported
in the literature. Default Smagorinsky model coefficients were used, and the LES
filter width was set as the cube root of the local cell volume. The tip speed
ratio was set to oscillate sinusoidally about $\lambda_0$ with a 0.19 magnitude
and the angle of the first peak at 1.4 radians---similar to the rotation
presribed in the blade-resolved RANS simulations discussed in
\cite{Bachant2016-BR-CFD}.
